---
title: "Data QCQA" 
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'DSM_data_QCQA.html')) })
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---
<!-- NOTES: 
1) Make sure to update file name in knit above (e.g., BB2_data_QCQA.html) 
2) Update ini file (e.g., BB2_data_QCQA.R) -->

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
library(knitr)
library(lubridate)
library(hms)
library(gridExtra)
library(amerifluxr)
library(heatmaply)
library(data.table)
library(ggpmisc)
```

```{r echo=FALSE}
# Comments/Notes
# 1) See if want to update sonic, temperature, and rad plots using multiple_plotlys

# 2) NEED TO ADD 7200, 7700 temp and 7200 RH & CHECK WHICH TEMP IS USED TO SONIC (cross wind corrected or no) ADD HERE after MEETING ON THURSDAY!
# 3) Try to track down WD_CUP at all sites
# 4) Remove duplicate variables (e.g., see google sheets for tracking)
# 5) Think about output directory (can change by replacing 'dirname(inputFile)' above)
# 6) Add EBC
```

<!-- specify init file to read -->
```{r echo=FALSE, include=FALSE}
read_chunk('ini_files/DSM_v2_data_QCQA.R')
```

```{r, echo=FALSE, include=FALSE}
<<LoadData>>
```

Sonic data 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Sonic variables and diagnostics

```{r}
sonic_plots(data,vars_WS,vars_WD,vars_other_sonic,units_other_sonic,pitch_ind)
```

Column {data-width=400}
-----------------------------------------------------------------------

### mean wind speed vs. u*
```{r}
scatter_plot_QCQA(data,vars_WS[1],vars_other_sonic[1],
                  "WS (m/s)","USTAR (m/s)",0)
```

### sigma_w vs. u*
```{r}
scatter_plot_QCQA(data,vars_other_sonic[1],
                  wind_std,
                  "USTAR (m/s)","W_SIGMA (m/s)",0)
```

Temp/RH 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Air and RH temperature comparison 
```{r}
temp_RH_plots(data,vars_temp,vars_RH)
```

Column {data-width=400}
-----------------------------------------------------------------------

### Temperature scatterplot
```{r}
scatter_plot_QCQA(data,vars_temp[1],vars_temp[2],"HMP Air temperature (°C)","Other Air Temperature (°C)",0)
```

### RH HMP vs. RH 7200

```{r}
scatter_plot_QCQA(data,vars_RH[1],vars_RH[2], "HMP RH (%)","LI-7200 RH (%)",0)
```

Radiation Time Series 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Radiation timeseries  
```{r}
radiation_plots(data,vars_radiometer,vars_NETRAD,vars_PPFD,var_potential_rad)
```

Column {data-width=400}
-----------------------------------------------------------------------

### SW_IN vs PPDF_IN
```{r}
scatter_plot_QCQA(data,vars_radiometer[1],vars_PPFD[1], "SW_IN (W/m2)","PPFD_IN (µmolPhoton/m2/s1)",0)
```

### SW_OUT vs PPFD_OUT

```{r}
scatter_plot_QCQA(data,vars_radiometer[2],vars_PPFD[2], "SW_OUT (W/m2)","PPFD_OUT (µmolPhoton/m2/s1)",00)
```

Radiation Diagnostics
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Checking for offsets with potential radiation  
```{r}
# CREATE FUNCTION!!
p <- ggplot() +
  geom_point(data = diurnal.composite, aes(x = time, y = potential_radiation), color = "steelblue",size = 0.5) +
  geom_point(data = diurnal.composite, aes(x = time, y = SW_IN), color = "red",linetype="dashed",size = 0.5) +
  geom_point(data = diurnal.composite, aes(x = time, y = exceeds), color = "black",size = 0.75)+
  scale_x_datetime(breaks="6 hours", date_labels = "%R")

p <- ggplotly(p+ facet_wrap(~as.factor(firstdate))) %>% toWebGL()
p
```

Column {data-width=400}
-----------------------------------------------------------------------

### Cross correlation analysis
```{r}
# CREATE FUNCTION!!
# Calculate % of instances when SW_IN > potential_radiation (for daytime only)

# Find daytime indices
ind_day <- which(diurnal.composite$SW_IN > 20)

# Find periods when SW_IN > potential_radiation
ind_exceeds <- which(diurnal.composite$SW_IN[ind_day] > diurnal.composite$potential_radiation[ind_day])

exceeds <- length(ind_exceeds)/length(ind_day)*100

ccf_obj <- ccf(diurnal.composite$potential_radiation, diurnal.composite$SW_IN)

Find_Max_CCF<- function(a,b)
{
  d <- ccf(a, b, plot = FALSE)
  cor = d$acf[,,1]
  lag = d$lag[,,1]
  res = data.frame(cor,lag)
  res_max = res[which.max(res$cor),]
  return(res_max)
}

Find_Max_CCF(diurnal.composite$potential_radiation[is.finite(diurnal.composite$potential_radiation)], diurnal.composite$SW_IN[is.finite(diurnal.composite$SW_IN)])
```


Pressure 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Pressure 
```{r}
# Barometric pressure 
#plotly_loop(data,vars_pressure,"Barometric pressure (kPa)")
```

Column {data-width=400}
-----------------------------------------------------------------------

### Pressure comparison (Met PA vs EC PA)
```{r}

```

Other met {data-orientation=rows} 
=======================================================================
Row {data-height=600}
-------------------------------------

### Additional meteorological variables

```{r}
multiple_plotly_plots(data,var_other,yaxlabel_other)
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}
```   
    
### Chart 3

```{r}
```